Finding the Most Suitable Code Clone Refactoring Techniques by Mapping Clone Context

### 2019-12-03 cefp/paper.tex
Working on conclusion

If clone instances share a common class, no further refactoring techniques are required. If they are in the same inheritance hierarchy, ``Pull-Up Method'' can be used till the extracted method is in a location accessible by all instances. If the instances share a common interface, some languages allow to move the extracted method there. Otherwise, if the clone instances are not related, we either have to create a superclass/interface abstaction or create an utility class to put the common functionality.

@@

\section{Conclusion}
To determine which refactoring techniques are most suitable to refactor most clones, we analyzed their context. We measured the \textbf{relation} through inheritance of clone instances in a clone class. In our corpus, we found that 37\% of clones are found in the same class. 24\% of clones are in the same inheritance hierarchy. Another 24\% of clones are unrelated. The final 15\% of clones have the same interface. We also looked at the \textbf{location} of clones: 78\% of clones are found at method-level of which 77\% is found in the body of a method or constructor.

>>>>

If clone instances share a common class, no further refactoring techniques are required. If they are in the same inheritance hierarchy, ``Pull-Up Method'' can be used till the extracted method is in a location accessible by all instances. If the instances share a common interface, some languages allow to move the extracted method there. Otherwise, if the clone instances are not related, we either have to create a superclass/interface abstraction or create a utility class to put the common functionality.

@@

\section{Conclusion}
We defined categories to argue about the contextual information of code clones. These categories are:
\begin{itemize}
  \item \textbf{Clone Relation}: The relation between clone instances among each other in a clone class.
  \item \textbf{Clone Location}: The location of clone instances in the codebase.
  \item \textbf{Clone Contents}: The contents of clone instances in the codebase.
\end{itemize}
For each category we propose subcategories,

To determine which refactoring techniques are most suitable to refactor most clones, we analyzed their context. We measured the \textbf{relation} through inheritance of clone instances in a clone class. In our corpus, we found that 37\% of clones are found in the same class. 24\% of clones are in the same inheritance hierarchy. Another 24\% of clones are unrelated. The final 15\% of clones have the same interface. We also looked at the \textbf{location} of clones: 78\% of clones are found at method-level of which 77\% is found in the body of a method or constructor.
